---
title: "GARCH-Analysis"
author: "Blaisonyl"
date: "5/9/2022"
output: word_document
---
load some libraries for the analysis
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rugarch)
library(xts)#for timeseries object coercion
library(quantmod)
library(ggplot2)
library(broom)
library(tidyverse)
library(dplyr)
```

```{r}
#global
options(scipen = 100, digits = 4)
```


Read the data
```{r cars}
data = read.csv("C:/Users/Blaisonyl/Downloads/datalabcovid.csv")
#data2 = read.csv("C:/Users/Blaisonyl/Downloads/ChiaraCOVID.csv")
```

Get the necessary data and clean it

```{r pressure, echo=FALSE}
data_cleaned <-data[2:828, ]
data_cleaned$Date <- as.Date(data_cleaned$Date, "%m/%d/%Y") # Note the Y instead of y. Our interest is a 4digit year char.
#data_cleaned["date.ts"] <- as.Date(data_cleaned$Date, "%m/%d/%Y")
```

Create a time series object
```{r}
data_ts <- xts(data_cleaned$Total_new_cases, data_cleaned$Date)
data_ts1 <- xts(data_cleaned$Total_new_cases, data_cleaned$Date)
class(data_ts) #Verify timeseries object
plot(data_ts)#roughly check the nature of our dataset
```

Fix and tidy time series data
```{r}
colnames(data_ts) <- c('cases') #help with tidying the dataset
data_ts <- tidy(data_ts) #clean the house for plotting
```

Plot the data
```{r}

ggplot(data_ts, aes(x = index, y = value, color = series))+ 
  geom_line() + 
  theme_bw() +
  labs(title = "Daily cases of COVID from January 2020 to April 2022", x = "Date", y = "Cases")

```

Due to the scale of the graph, we might be tempted to think its a constant
Trend till end of 2021, for this reason, i thought to look closely at 2020 - 2021 data to appreciate the underlying trends


2020 data
```{r}
data2020 <- data_cleaned[1:348, ]
data2020_ts <- xts(data2020 $Total_new_cases, data2020 $Date)
colnames(data2020_ts) <- c('cases')
data2020_ts <- tidy(data2020_ts)
ggplot(data2020_ts, aes(x = index, y = value, color = series))+ 
  geom_line() + 
  theme_bw() +
  labs(title = "Daily cases of COVID from January 2020 to December 2020", x = "Date", y = "Cases")

```

2021-2022 data
```{r}

data2021_2022 <- data_cleaned[349:713, ]
data2021_2022_ts <- xts(data2021_2022 $Total_new_cases, data2021_2022$Date)
colnames(data2021_2022_ts) <- c('cases')
data2021_2022_ts <- tidy(data2021_2022_ts)
ggplot(data2021_2022_ts, aes(x = index, y = value, color = series))+ 
  geom_line() + 
  theme_bw() +
  labs(title = "Daily cases of COVID from January 2021 to December 2021", x = "Date", y = "Cases")

```

2020-2022 data
```{r}

data2020_2022 <- data_cleaned[1:713, ]
data2020_2022_ts <- xts(data2020_2022 $Total_new_cases, data2020_2022$Date)
colnames(data2020_2022_ts) <- c('cases')
data2020_2022_ts <- tidy(data2020_2022_ts)
ggplot(data2020_2022_ts, aes(x = index, y = value, color = series))+ 
  geom_line() + 
  theme_bw() +
  labs(title = "Daily cases of COVID from January 2020 to January 2022", x = "Date", y = "Cases")

```

As we can see there are underlying differences in trends 

GARCH model
Note, We will do a couple of GARCH models and chose which to use based on the lowest AKAIKE value
In the next lines i attemt to change the armaorder, variance model and the distribution.model arguments
to obtain the model with the best fit 

GARCH model for current day and error term of current day
AIM to Chose the GARCH model with lowest AIC number AKA AKAIKE

```{r}
Garch_02 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
                       mean.model = list(armaOrder = c(1, 1), include.mean = TRUE), 
                       distribution.model = "std", fixed.pars = list(omega = 0))

garch_result<- ugarchfit(spec = Garch_02, data = data_ts$value, solver = "hybrid")
garch_result  ##13.401 best
```

This i think is the best garch model. and the best till the end of the script.


Plot the prediction graph
```{r}
Predict <- ugarchboot(garch_result, n.ahead = 30, method = c("Partial", "Full")[1])
plot(Predict, which = 2)
#forcasts show that upper limits top dots, and lower limits bottom dots. 

```
Just to see how the actual predicted values look on a plot
```{r}
plot(Predict@forc, which = 1)
```

closer look
```{r}
plot(Predict@forc, which = 3)
```


```{r}
Garch_02 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
                       mean.model = list(armaOrder = c(1, 1), include.mean = TRUE), 
                       distribution.model = "std", fixed.pars = list(omega = 0))

garchfit<- ugarchfit(spec = Garch_02, data = data_ts$value, solver = "hybrid")
garchfit

```

```{r}
plot(garchfit, which = 2)
```


Plot a forcast graph
```{r}
spec <- getspec(garchfit)
setfixed(spec) <- as.list(coef(garchfit))
#pars <- spec@model$fixed.pars
GarchForcast <- ugarchforecast(spec, data = data_ts1, n.roll = 826, n.ahead = 30, out.sample =826)

```

```{r}
df <- c(data_cleaned$Total_new_cases)
```


```{r}
plot(GarchForcast, which = 4, lwd = 6.0)
```
Preprocess Data

```{r}
Region_data <- data_cleaned
columnnames<-colnames(Region_data)[-1]

for (a in columnnames) {
  suppressWarnings(Region_data[[a]] <- as.numeric(Region_data[[a]]) )
}

Region_data[is.na(Region_data)] <-0
```

Load region data

```{r}

Region_data$region1 <- rowSums(Region_data[, c("Seoul", "Incheon", "Gyeongi")], na.rm = TRUE)
Region_data$region2 <- rowSums(Region_data[, c("Busan", "Daegu", "Gwangju", "Daejeon", "Ulsan", "Sejeon", "Kangwon", "Chungbuk", "Chungnam", "Jeonbuk", 
"Jeonnam", "Gyeongbuk", "Gyeongnam", "Jeju")], na.rm = TRUE)

```


```{r}
data_ts_R1 <- xts(Region_data$region1, Region_data$Date)
data_ts_R2 <- xts(Region_data$region2, Region_data$Date)
```

Region 1 forecast
```{r}
GarchForcast1 <- ugarchforecast(spec, data = data_ts_R1, n.roll = 826, n.ahead = 30, out.sample =826)

```

```{r}
plot(GarchForcast1, which = 4)
```


Region 2 forecast
```{r}
GarchForcast2 <- ugarchforecast(spec, data = data_ts_R2, n.roll = 826, n.ahead = 30, out.sample =826)
plot(GarchForcast2, which = 4)
```


































